Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
tex

\subsection{Potential Societal Impact.}

@@

\subsection{Limitations.}

@@

\section{More Technical and Design Details}
\label{sec:b}

\noindent\textbf{I. Hardware and Software Platform.}

We conduct the experiments with two Nvidia Titan Xp GPUs under the Ubuntu 16.04
operating system with PyTorch 1.8.2 in distributed data parallel mode.

~\newline
\noindent\textbf{II. Embedding-Shifted Triplet (EST).}~\cite{advrank}

@@

~\newline
\noindent\textbf{III. Anti-Collapse Triplet (ACT).}~\cite{robrank}

@@

~\newline
\noindent\textbf{IV. Hardness Manipulation (HM).}

>>>>

\subsection{Potential Societal Impact}

@@

\subsection{Limitations of Our Method}

@@

\section{More Technical Details}
\label{sec:b}

\subsection{Hardware and Software Platform}

We conduct the experiments with two Nvidia Titan Xp GPUs (12GB of memory each)
under the Ubuntu 16.04 operating system with PyTorch 1.8.2 in distributed data
parallel mode.

\subsection{State-of-The-Art Defenses}

\noindent\textbf{I. Embedding-Shifted Triplet (EST).}~\cite{advrank}

@@

~\newline
\noindent\textbf{II. Anti-Collapse Triplet (ACT).}~\cite{robrank}

@@

\subsection{Hardness Manipulation (HM)}

\oo{todo}
